Bow shocks, bow waves, and dust waves. III. Diagnostics

### 2019-06-21 papers/Papers1234/sigma-ori-arcs.tex
Finish intro to paper II
New amateur images of sigma Ori

\title
% {No radiation supported dust wave around \(\sigma\) Orionis}
% OR
{\boldmath A dusty bow shock around \(\sigma\) Orionis driven by an enclosed proplyd?}

@@

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  We critically evaluate the role of radiation and hydrodynamics in
  providing internal support for the bow-shaped infrared arc around
  the massive triple star system \(\sigma\)~Ori Aa/Ab/B in the IC434 \hii{}
  region.  We present evidence for hydrogen recombination line
  emission from the arc, which demonstrates that it cannot be a
  decoupled dust wave, as has previously been claimed.  On the other
  hand, we show that the fraction of the stellar luminosity trapped by
  the arc is insufficient for it to be supported by radiation if the
  grains and gas are well coupled.  Therefore, the arc must be
  supported by the ram pressure of an internal wind.  However, the
  stellar winds from the OB stars in the \(\sigma\)~Ori Aa/Ab/B system seem
  too weak to provide this support on their own.  We propose instead
  that it is the photoevaporated disk wind from the enclosed proplyd
  IRS~1B that dominates the ram pressure support for the bow.
\end{abstract}

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/sigma-ori-comparison}
  \caption{Optical and infrared images of $\sigma$~Ori}
  \label{fig:sig-ori}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/sigma-ori-eastwest-cuts}
  \caption{Brightness profiles through $\sigma$~Ori inner arc.}
  \label{fig:sig-ori-cuts}
\end{figure}

@@

>>>>

\title
% {No radiation supported dust wave around \(\sigma\) Orionis}
% OR
% {\boldmath A dusty bow shock around \(\sigma\) Orionis driven by an enclosed proplyd?}
% OR
{\boldmath Bow shocks, bow waves, and dust waves. V. No dust wave for \(\sigma\) Ori}

@@

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  We critically evaluate the role of radiation and ram pressure in
  providing internal support for the bow-shaped infrared arc around
  the massive triple star system \(\sigma\)~Ori Aa/Ab/B in the IC434 \hii{}
  region.  We present evidence for hydrogen recombination line
  emission from the arc, which demonstrates that it cannot be a
  decoupled dust wave, as has previously been claimed.  On the other
  hand, we show that the fraction of the stellar luminosity trapped by
  the arc is insufficient for it to be supported by radiation if the
  grains and gas are well coupled.  Therefore, the arc must be
  supported by the ram pressure of an internal wind.  However, the
  stellar winds from the OB stars in the \(\sigma\)~Ori Aa/Ab/B system seem
  too weak to provide this support on their own.  We propose instead
  that it is the photoevaporated disk wind from the enclosed proplyd
  IRS~1B that dominates the ram pressure support for the bow.
\end{abstract}

@@

We downloaded optical images of \(\sigma\)~Ori from the Astronomical Data
Centre of the Cambridge Astronomy Survey
Unit.\footnote{\url{http://casu.ast.cam.ac.uk/surveys-projects/adc}}
These were obtained on 2008-11-19 with the Wide Field Camera of the
Isaac Newton Telescope from an observational program of Rafael
Barrena.  We use images in two filters: a narrow-band H\(\alpha\) filter
(central wavelength, \(\lambda_0 = \SI{656.8}{nm}\), full-width half
maximum, \(\Delta\lambda = \SI{9.5}{nm}\)) and a broad-band Sloan Gunn
\(R\) filter (\(\lambda_0 = \SI{624.0}{nm}\), \(\Delta\lambda = \SI{134.7}{nm}\)).  We have removed the bias v

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/sigma-ori-comparison}
  \caption{Optical and infrared images of $\sigma$~Ori and its
    surroundings.  (a)~Optical image in in the H\(\alpha\) line, shown in
    negative grayscale.  (b)~Mid-infrared image in three Spitzer
    bands: MIPS \SI{23.7}{\um} (red), IRAC \SI{7.87}{\um} (green), and
    IRAC \SI{5.73}{\um} (blue).  The yellow dashed box shows the slit
    for which profiles are extracted in Fig.~\ref{fig:sig-ori-cuts}.}
  \label{fig:sig-ori}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/sigma-ori-eastwest-cuts}
  \caption{Brightness profiles through $\sigma$~Ori inner arc.  (a)~H\(\alpha\) and  All
    profiles are extracted in a \(40''\) wide slit, offset by \(80''\)
    to the south of \(\sigma\)~Ori, as indicated in
    Fig.~\ref{fig:sig-ori}b. }
  \label{fig:sig-ori-cuts}
\end{figure}

@@

\section*{Acknowledgements}

We are grateful for financial support provided by Dirección General de
Asuntos del Personal Académico, Universidad Nacional Autónoma de
México, through grant Programa de Apoyo a Proyectos de Investigación e
Inovación Tecnológica IN107019.  We thank Bo Reipurth for advice on
astronomical data archives.  This work is based in part on
observations made in the Observatorios de Canarias del IAC with the
Isaac Newton Telescope operated on the island of La Palma by the
Instituto de Astrofísica de Canarias in the Observatorio del Roque de
los Muchachos. 
% Based in part on observations made with the Isaac Newton Telescope
% under Director’s Discretionary Time of Spain’s Instituto de
% Astrofísica de Canarias.
This work is based in part on observations made with the Spitzer Space
Telescope, which is operated by the Jet Propulsion Laboratory,
California Institute of Technology under a contract with NASA.\@ This
work makes use of imagery from David Mittelman Astrophotography.
